A new form of transcorrelated Hamiltonian inspired by range-separated DFT

### 2021-04-13 cusp_j/paper/paper_draft.tex
added plot_on_top_z.irp.f in Yuan
fixed a stupid bug in fcidump_tc_h_3_body_sym.irp.f with active indices

\section{Derivation with a varying $\mu({\bf r})$}
Let us assume one has a range separation parameter varying in space $\mur{}$ and that one knows its gradients and Laplacian. 
Therefore, one would like to derive the same equations as for the constant $\mu$. 
The Jastrow factor is therefore expressed as
\begin{equation}
 \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( u(r_{12};\mur{1}) + u(r_{12};\mur{2}) \bigg)
\end{equation}
where $u(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
To derive properly the equations for such a new Jastrow factor, one needs to derive the different terms involving gradients and so on. 
\subsection{Gradients of $\tilde{u}(\bd{r_1},\bd{r_2})$}
A fundamental quantity is the gradient of $\tilde{u}(\bd{r_1},\bd{r_2})$ which is 
\begin{equation}
 \nabla_1 \tilde{u}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
\end{equation}
Therefore one needs to compute $\deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2})$
\begin{equation}
 \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{1}) 
                                               +\frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{2}) .
\end{equation}
Let us begin with the first term 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} u(r_{12};\mur{1})=& \deriv{}{r_{12}}{} u(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} \\ 
                                  +& \deriv{}{\mur{1}}{}u(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
 \end{aligned}
\end{equation}
but as 
\begin{equation}
 \deriv{}{\mu}{}u(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2 \sqrt{\pi} \mu^2}
\end{equation}
one obtains 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
 \end{aligned}
\end{equation}
Similarly, as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
of the condition determining $u(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
\begin{equation}
 \deriv{}{x_1}{} u(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
\end{equation}
Therefore, one obtains finally that 
\begin{equation}
 \label{eq:d_dx1_jtilde}
 \begin{aligned}
 \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
 \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
                 & + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{},
 \end{aligned}
\end{equation}
and similarly,
\begin{equation}
 \label{eq:d_dx2_jtilde}
 \begin{aligned}
 \deriv{}{x_2}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
 \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
                 & + \frac{e^{-(\mur{2} r_{12})^2}}{2\sqrt{\pi} \mur{2}^2} \deriv{\mur{2}}{x_2}{},
 \end{aligned}
\end{equation}

@@

Summing all terms and noticing that $\bigg(x_1 - x_2\bigg)^2 + \bigg(y_1 - y_2\bigg)^2 + \bigg(z_1 - z_2\bigg)^2 = \bigg(r_{12}\bigg)^2$ leads to 
\begin{equation}
 \begin{aligned}
& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = 
  \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
&+\frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{4 \sqrt{\pi}r_{12}}  \\
& \big( \bri{1} - \bri{2}\big)\cdot
\bigg(\frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
  -   \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
  &+ \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
 + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
 \end{aligned}
\end{equation}
\bibliography{srDFT_SC}

% f(x) = (3*erf(mu*x) - 1)/(2*x) + 1.5*mu/sqpi * exp(-(mu*x)**2.) - 0.25 * (1 - erf(mu*x))**2.

\section{Form of the adjoint operator}
One can write $\tilde{H}[\mu]$ in terms of its hermitian and non hermitian parts 
\begin{equation}
 \tilde{H}[\mu] = \tilde{H}^h[\mu] + \tilde{H}^{nh}[\mu]
\end{equation}
where the hermitian part is 
\begin{equation}
 \tilde{H}^h[\mu] = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) 
\end{equation}
with 
\begin{equation}
 \Delta_1 u(r_{12},\mu) = \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} - \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2},
\end{equation}
\begin{equation}
 \big( \nabla_1 u(r_{12},\mu)\big)^2 = \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}, 
\end{equation}
and 
\begin{equation}
 \tilde{H}^{nh}[\mu] = \nabla_{1}u(r_{12},\mu) \cdot \big(\nabla_1 - \nabla_2\big)
\end{equation}
The adjoint of the non hermitian operator $\tilde{H}^{nh}[\mu]$ is 
\begin{equation}
 \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger =  \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger - \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger,
\end{equation}
with 
\begin{equation}
 \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_1 
                                                                - \nabla_1^2 u(r_{12},\mu)
\end{equation}
\begin{equation}
 \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
                                                                - \nabla_1 \cdot \nabla_2 u(r_{12},\mu)
\end{equation}
but as 
\begin{equation}
 \nabla_2 u(r_{12},\mu) = - \nabla_{1}u(r_{12},\mu)
\end{equation}
one has
\begin{equation}
 \nabla_1 \cdot \nabla_2 u(r_{12},\mu) = - \nabla_1^2 u(r_{12},\mu)
\end{equation}
and therefore 
\begin{equation}
 \bigg( \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 \bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \nabla_2 
                                                                + \nabla_1^2 u(r_{12},\mu)
\end{equation}
which gives for the adjoint of the non hermitian operator 
\begin{equation}
 \bigg( \tilde{H}^{nh}[\mu]\bigg)^\dagger = - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu).
\end{equation}
Therefore the adjoint of the TC Hamiltonian is
\begin{equation}
 \begin{aligned}
\bigg(\tilde{H}[\mu]\bigg)^\dagger & = \tilde{H}^h[\mu] + \bigg( \tilde{H}^{nh}[\mu] \bigg)^\dagger \\
                                   & = \tilde{H}^h[\mu]  - \nabla_{1}u(r_{12},\mu) \cdot \big( \nabla_1 -\nabla_2 \big) - 2 \nabla_1^2 u(r_{12},\mu)  \\
                                   & = \tilde{H}^h[\mu]  - \tilde{H}^{nh}[\mu] - 2 \nabla_1^2 u(r_{12},\mu) 
 \end{aligned}
\end{equation}
Then 
\begin{equation}
 \begin{aligned}
 \frac{\tilde{H}[\mu] + \bigg(\tilde{H}[\mu]\bigg)^\dagger}{2}& = \tilde{H}^h[\mu] - \nabla_1^2 u(r_{12},\mu) \\
                                                              & = H - \bigg( \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) - \nabla_1^2 u(r_{12},\mu) \\
                                                              & = H - \bigg( 2 \Delta_1 u(r_{12},\mu) + \big( \nabla_1 u(r_{12},\mu)\big)^2\bigg) \\
                                                              & = h_c + \frac{1}{r_{12}} - 2 \frac{1 - \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2} 
                                                                 - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4} \\
                                                              & = h_c - \frac{1 - 2 \text{erf}(\mu r_{12})}{r_{12}} + 2 \frac{\mu}{\sqrt{\pi}} e^{-\big(\mu r_{12} \big)^2}  - \frac{\bigg(1 - \text{erf}(\mu r_{12})\bigg)^2}{4}
 \end{aligned}
\end{equation}

>>>>

\section{Derivation with a varying $\mu({\bf r})$}
Let us assume one has a range separation parameter varying in space $\mur{}$ and that one knows its gradients and Laplacian. 
Therefore, one would like to derive the same equations as for the constant $\mu$. 
The Jastrow factor is therefore expressed as
\begin{equation}
 \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\bigg( u(r_{12};\mur{1}) + u(r_{12};\mur{2}) \bigg)
\end{equation}
where $u(r_{12};\mu)$ is the Jastrow factor defined in Eq. \eqref{eq:def_j}. 
To derive properly the equations for such a new Jastrow factor, one needs to derive the different terms involving gradients and so on. 
\subsection{Gradients of $\tilde{u}(\bd{r_1},\bd{r_2})$}
A fundamental quantity is the gradient of $\tilde{u}(\bd{r_1},\bd{r_2})$ which is 
\begin{equation}
 \nabla_1 \tilde{u}(\bd{r_1},\bd{r_2}) = \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{y_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{y1} + \deriv{}{z_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) {\bf e}_{z1}.
\end{equation}
Therefore one needs to compute $\deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2})$
\begin{equation}
 \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = \frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{1}) 
                                               +\frac{1}{2}\deriv{}{x_1}{} u(r_{12};\mur{2}) .
\end{equation}
Let us begin with the first term 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} u(r_{12};\mur{1})=& \deriv{}{r_{12}}{} u(r_{12};\mur{1})\deriv{r_{12}}{x_1}{} \\ 
                                  +& \deriv{}{\mur{1}}{}u(r_{12};\mur{1}) \deriv{\mur{1}}{x_1}{},
 \end{aligned}
\end{equation}
but as 
\begin{equation}
 \deriv{}{\mu}{}u(r_{12};\mu) = \frac{e^{-(\mu r_{12})^2}}{2 \sqrt{\pi} \mu^2}
\end{equation}
one obtains 
\begin{equation}
 \begin{aligned}
  \label{eq:grad_mur_1}
 \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
 \end{aligned}
\end{equation}
Similarly, as by definition $\deriv{\mur{2}}{x_1}{} = 0$, because 
of the condition determining $u(r_{12};\mu)$ (see Eq.\eqref{def_j_0}) and according to Eq.\eqref{eq:dx1_u} one obtains that 
\begin{equation}
 \deriv{}{x_1}{} u(r_{12};\mur{2}) = \frac{1 - \text{erf}(\mur{2} r_{12})}{2 r_{12}} \bigg(x_1 - x_2 \bigg).
\end{equation}
Therefore, one obtains finally that 
\begin{equation}
 \label{eq:d_dx1_jtilde}
 \begin{aligned}
 \deriv{}{x_1}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_1 - x_2)}{2 r_{12}} 
 \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
                 & + \frac{e^{-(\mur{1} r_{12})^2}}{2\sqrt{\pi} \mur{1}^2} \deriv{\mur{1}}{x_1}{},
 \end{aligned}
\end{equation}
and similarly,
\begin{equation}
 \label{eq:d_dx2_jtilde}
 \begin{aligned}
 \deriv{}{x_2}{} \tilde{u}(\bd{r_1},\bd{r_2}) = & \frac{(x_2 - x_1)}{2 r_{12}} 
 \bigg( \frac{1 - \text{erf}(\mur{1} r_{12})}{2} + \frac{1 - \text{erf}(\mur{2} r_{12})}{2}  \bigg) \\
                 & + \frac{e^{-(\mur{2} r_{12})^2}}{2\sqrt{\pi} \mur{2}^2} \deriv{\mur{2}}{x_2}{},
 \end{aligned}
\end{equation}

@@

Summing all terms and noticing that $\bigg(x_1 - x_2\bigg)^2 + \bigg(y_1 - y_2\bigg)^2 + \bigg(z_1 - z_2\bigg)^2 = \bigg(r_{12}\bigg)^2$ leads to 
\begin{equation}
 \begin{aligned}
& \bigg(\nabla_1\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 + \bigg(\nabla_2\tilde{u}(\bd{r_1},\bd{r_2})\bigg)^2 = 
  \frac{1}{8}\bigg(\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big) \bigg)^2  \\
&+\frac{\text{erfc}\big(\mur{1} r_{12}\big) + \text{erfc}\big(\mur{2} r_{12}\big)}{4 \sqrt{\pi}r_{12}}  \\
& \big( \bri{1} - \bri{2}\big)\cdot
\bigg(\frac{e^{- \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \nabla_1 \mur{1}
  -   \frac{e^{- \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \nabla_2 \mur{2}  \bigg) \\
  &+ \frac{e^{-2 \,\big(\mur{1}r_{12} \big)^2}}{4\pi \big(\mur{1}\big)^4} \bigg( \deriv{}{x_1}{}\mur{1} \bigg)^2 
 + \frac{e^{-2 \,\big(\mur{2}r_{12} \big)^2}}{4\pi \big(\mur{2}\big)^4} \bigg( \deriv{}{x_2}{}\mur{2} \bigg)^2.
 \end{aligned}
\end{equation}
\bibliography{srDFT_SC}

% f(x) = (3*erf(mu*x) - 1)/(2*x) + 1.5*mu/sqpi * exp(-(mu*x)**2.) - 0.25 * (1 - erf(mu*x))**2.
\subsection{Proposal of an ad-hoc symmetrization}
Let us assume that we only take a non symmetric form 
\begin{equation}
 \tilde{u}(\bd{r_1},\bd{r_2}) = u(r_{12};\mur{1}), 
\end{equation}
and we will see afterwards how to symmetrize the Hamiltonian.
\subsubsection{Computation of $\bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2$ }
therefore, according to Eq. \eqref{eq:grad_mur_1} one has 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} u(r_{12};\mur{1}) =& \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \\
                                   +&\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.  
 \end{aligned}
\end{equation}
Therefore, the computation of $\big( \deriv{}{x_1}{} u(r_{12};\mur{1}) \big)^2$ yields 
\begin{equation}
 \begin{aligned}
 \bigg( \deriv{}{x_1}{} u(r_{12};\mur{1}) \bigg)^2 = & \frac{\bigg(1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)\bigg)^2}{4 \big(r_{12}\big)^2}\big( x_1 - x_2)^2 \\
 + & \frac{e^{-2(\mu(\bri{1}) r_{12})^2}}{4 \pi \mu(\bri{1})^4} \bigg(\deriv{\mur{1}}{x_1}{} \bigg)^2 \\ 
 + & \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{r_{12}}\big( x_1 - x_2) \frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{}.
 \end{aligned}
\end{equation}
Therefore, the computation of $\bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2$ yields 
\begin{equation}
 \begin{aligned}
  \bigg( \nabla_1  u(r_{12};\mur{1})\bigg)^2  = &\frac{\bigg(1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)\bigg)^2}{4} 
   +   \frac{e^{-2(\mu(\bri{1}) r_{12})^2}}{4 \pi \mu(\bri{1})^4} \bigg( \nabla_1  \mur{1}\bigg)^2 \\ 
   + & \nabla_1  \mur{1} \, \cdot \, \big( \br{}_1 - \br{}_2\big) \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{r_{12}} \frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi}\mu(\bri{1})^2} 
 \end{aligned}
\end{equation}

\subsubsection{Computation of $\nabla_1^2  u(r_{12};\mur{1})$ }
One has to perform first 
\begin{equation}
 \begin{aligned}
  \deriv{}{x_1}{2} u(r_{12};\mur{1}) =  & \deriv{}{x_1}{}  \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \bigg) \\ 
      + & \deriv{}{x_1}{}  \bigg(\frac{e^{-(\mu(\bri{1}) r_{12})^2}}{2 \sqrt{\pi} \mu(\bri{1})^2} \deriv{\mur{1}}{x_1}{} \bigg).
 \end{aligned}
\end{equation}
Let us begin with the first term 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{}  \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}\big( x_1 - x_2) \bigg)  = 
&  \big( x_1 - x_2 \big) \deriv{}{x_1}{} \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \bigg) \\
+ & \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}}.
 \end{aligned}
\end{equation}
Then on has that 
\begin{equation}
 \begin{aligned}
 \deriv{}{x_1}{} \bigg(\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \bigg) &= 
 \deriv{}{r_{12}}{} \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{r_{12}}{x_1}{} \\  
 & + \deriv{}{\mur{1}}{}\frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{\mur{1}}{x_1}{}.
 \end{aligned}
\end{equation}
The first term reads 
\begin{equation}
 \begin{aligned}
& \deriv{}{r_{12}}{} \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} \deriv{r_{12}}{x_1}{} = \\
& -\frac{(x_1 - x_2)}{\big(r_{12}\big)^2} \bigg( \frac{1 - \text{erf}\big(\mu(\bri{1}) r_{12} \big)}{2 r_{12}} + \frac{\mu(\br{}_1)}{\sqrt{\pi}} e^{-\big(\mu(\br{}_1) r_{12}\big)^2}\bigg).  
 \end{aligned}
\end{equation}
